Improving Day Ahead Electricity Load Forecasts with Google Trends

### 2014-07-29 Paper/DraftPaper.Rnw
Added figure that shows the google weather searches are significant for all hours.

@@

<<echo=false, results=tex>>=

for(x in 13:24){
  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
}
@

>>>>

\begin{figure}
\begin{center}
\caption{Confidence Intervals for ``Weather'' in Trends Models (95\%)}
<<echo=false,fig=TRUE>>=
library(ggplot2)

LowInter<-unlist(lapply(GrossTrends, FUN= function(x) confint(x) [3,1]))
HighInter<-unlist(lapply(GrossTrends, FUN= function(x) confint(x) [3,2]))
InterceptResults<-data.frame(1:24,LowInter,HighInter)
names(InterceptResults)[1]<-"Hour"

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Confidence Interval")
@
\end{center}
\end{figure}

@@

<<echo=false, results=tex>>=
for(x in 13:24){
  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
}
@
